---
title: "20181116a Lists of drugs"
author: "cheungngo"
date: "16 November 2018"
output: word_document
---

### Getting the lists of 'L-type Calcium channel antagonists'

From the paper: 'Targeting the schizophrenia genome: a fast track strategy from GWAS to clinic', the gene of interest would be CACNA1C and CACNB2 (grouped together as they encode component subunits of the same channel)  

CACNA1C: Voltage-dependent L-type calcium channel subunit alpha-1C  
CACNB2: Voltage-dependent L-type calcium channel subunit beta-2  

We extracted the data table from the drug bank. 

For CACNA1C:  
There are 25 entries in total  
8 removed because of unknown / no pharmacological actions  
'Ibutilide' removed as it is known to be an activator  
'Calcium' removed as it is known to be a ligand  
15 drugs left  

For CACNB2:  
There are 13 entries in total  
2 removed because of unknown / no pharmacological actions  
11 drugs left  

### Combining the two tables (for overlaps)  

```{r}
library(readxl)
L_type_calcium_channel_combined_pre <- read_excel("L-type calcium channel combined pre.xlsx")
pre = L_type_calcium_channel_combined_pre
```

```{r}
post = unique(pre)
dim(post)
head(post)
```

```{r, message=FALSE}
library(readr)
```

```{r}
write_csv(post, 'L-type calcium channel combined post.csv')
```
